---
title: "VELOOP Rewards — Giveaway Module"
subtitle: "Full Architecture & Development Roadmap"
author: "VELOOP Rewards"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: flatly
    number_sections: true
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
```

Frontend architecture, data flow design, and a week-by-week execution plan for the
Giveaway Page, Banner, Participation, and Winner system.

---

# Full Folder Architecture

The project is split into two phases with two top-level folders: **frontend/** (build
first, fully mock-data driven) and **backend/** (build second, once the frontend is
approved). The key rule throughout: every component reads from `data/` or
`services/` — never hardcodes a prize name, fee, or status directly.

```
veloop-giveaway/
|
+-- frontend/
|   +-- public/
|   |   +-- assets/                    (prize images, icons from provided assets)
|   |
|   +-- src/
|   |   +-- components/
|   |   |   +-- GiveawayHero/
|   |   |   +-- GiveawayBanner/
|   |   |   +-- Countdown/
|   |   |   +-- GiveawayStats/
|   |   |   +-- PrizeCard/
|   |   |   +-- FeaturedGiveaways/
|   |   |   +-- HowToParticipate/
|   |   |   +-- WinnerSlider/
|   |   |   +-- WinnersTabs/
|   |   |   +-- WinnerCard/
|   |   |   +-- PreviousWinnerCard/
|   |   |   +-- PrizeClaimModal/
|   |   |   +-- JoinConfirmModal/
|   |   |   +-- BalanceIndicator/
|   |   |   +-- GiveawayRules/
|   |   |   +-- FAQ/
|   |   |   +-- TrustSection/
|   |   |   +-- GiveawayLoader/         (custom themed loader, sec 51-55)
|   |   |   +-- EmptyState/
|   |   |   +-- ErrorState/
|   |   |   +-- Skeletons/
|   |   |
|   |   +-- pages/
|   |   |   +-- GiveawayHome/           (main listing page)
|   |   |   +-- GiveawayDetails/        (/giveaway/:slug - individual page)
|   |   |   +-- NotFound/
|   |   |
|   |   +-- data/
|   |   |   +-- giveawayData.js         (mock API-shaped data)
|   |   |   +-- mockSession.js          (fake logged-in user, balances)
|   |   |   +-- mockWinners.js
|   |   |
|   |   +-- hooks/
|   |   |   +-- useCountdown.js
|   |   |   +-- useGiveawayStatus.js
|   |   |   +-- useBalanceCheck.js
|   |   |   +-- useGiveaway.js          (later wraps real fetch calls)
|   |   |
|   |   +-- context/
|   |   |   +-- UserContext.jsx         (mock auth/session state)
|   |   |
|   |   +-- services/
|   |   |   +-- giveawayApi.js          (stub functions -> real fetch later)
|   |   |
|   |   +-- utils/
|   |   |   +-- currencyValidation.js   (VEs/SVEs/Tokens rules, sec 89)
|   |   |   +-- maskUserId.js           (VE****42 style masking)
|   |   |   +-- formatTime.js
|   |   |
|   |   +-- styles/                     (global CSS variables, tokens)
|   |   +-- App.jsx
|   |   +-- main.jsx
|   |
|   +-- vite.config.js
|
+-- backend/                            (Phase 2 - do not start yet)
    +-- src/
    |   +-- controllers/
    |   |   +-- giveawayController.js
    |   |   +-- participationController.js
    |   |   +-- winnerController.js
    |   |   +-- claimController.js
    |   |   +-- adminGiveawayController.js
    |   +-- models/
    |   |   +-- Giveaway.js
    |   |   +-- Prize.js
    |   |   +-- GiveawayParticipation.js
    |   |   +-- GiveawayEntryTransaction.js
    |   |   +-- GiveawayWinner.js
    |   |   +-- PrizeClaim.js
    |   |   +-- FraudEvent.js
    |   |   +-- AuditLog.js
    |   +-- routes/
    |   +-- middleware/
    |   |   +-- authMiddleware.js
    |   |   +-- rateLimitMiddleware.js
    |   |   +-- validationMiddleware.js
    |   |   +-- fraudMiddleware.js
    |   |   +-- errorMiddleware.js
    |   +-- services/
    |   |   +-- giveawayService.js
    |   |   +-- participationService.js
    |   |   +-- balanceService.js
    |   |   +-- fraudService.js
    |   |   +-- winnerService.js
    |   +-- utils/
    |   +-- validators/
    |   +-- config/
    |   +-- app.js
    +-- server.js
```

---

# State & Data Flow Design

## UserContext

Holds `isLoggedIn`, `currentUserId`, and `balances` (VEs, SVEs, Tokens). Fully
mocked for now; swapped for real auth once the backend exists.

## services/giveawayApi.js

Exports functions such as `getCurrentGiveaways()`, `getGiveawayBySlug()`,
`joinGiveaway()`, and `submitClaim()`. Right now they return mock data behind a
fake delay (to honestly test loading states). Later, only the function bodies
change to real `fetch()` calls — nothing else in the app needs to change.

## useGiveawayStatus(giveaway)

A single hook that is the one source of truth for `ACTIVE` / `ENDED` /
`UPCOMING`, used by every component instead of scattering status checks across
the codebase.

> **Architectural rule:** the frontend is built exactly as if a real backend
> already exists. Components never see raw hardcoded values — only data
> returned from the `data/` and `services/` layers. This is what allows Phase 2
> (backend integration) to be a drop-in swap instead of a rewrite.

---

# Roadmap

Suggested pace: 3–4 weeks for the frontend phase, followed by a separate
backend phase once the frontend is reviewed and approved.

## Week 1 — Foundation

- Scaffold project (Vite + React), install dependencies, build the folder skeleton
- Write `giveawayData.js` and `mockSession.js` with realistic, API-shaped data (sections 36–38, 85 of the task doc)
- Build `UserContext`, `useCountdown`, and `useGiveawayStatus` hooks
- Build the Hero / Banner section (static layout first, no live logic yet)

## Week 2 — Core Home Page

- Wire the Countdown component to the real hook
- Build the Statistics section, Prize Cards grid, and Winner Slider
- Build the How-to-Participate timeline, Trust section, and FAQ accordion
- Build Winners Tabs and Previous Winners Tabs, including the correct empty state for an active giveaway that has no winners yet (section 21)

## Week 3 — Individual Giveaway Page + Join Flow

- Set up routing for `/giveaway/:slug`
- Build the Prize Information card, entry-fee display, and balance-check UI
- Build the Join Confirmation modal, success state, and already-joined state
- Build the login-required redirect flow for unauthenticated users

## Week 4 — Winner / Claim System + Polish

- Winner detection: `currentUserId === winner.userId`
- Claim modal with branching logic for physical prize vs. gift-card form, based on `prize.type`
- Claim states: submitted, processing, completed, expired
- Loading skeletons, error states, and empty states across all sections
- Full responsive pass: mobile -> tablet -> desktop
- Accessibility pass: labels, visible focus states, keyboard navigation
- Write the README, capture screenshots, deploy to Vercel

## Phase 2 — Backend (after frontend is approved / submitted)

- Scaffold the backend, define MongoDB models, build auth middleware
- Build the join endpoint with transaction handling and fraud checks
- Build winner-selection and prize-claim endpoints
- Swap the mock functions in `services/giveawayApi.js` for real fetch calls — this should be close to a drop-in replacement if Phase 1 was structured correctly

## Summary

```{r roadmap-table}
roadmap <- data.frame(
  Week = c("1", "2", "3", "4", "Phase 2"),
  Focus = c("Foundation", "Home page", "Detail page", "Claim + polish", "Backend"),
  `Key Deliverables` = c(
    "Project scaffold, mock data model, hooks, static banner",
    "Countdown, stats, prize cards, winner slider, tabs, FAQ",
    "Routing, prize info, join confirmation, login gate",
    "Claim system, loaders, responsive + a11y pass, deploy",
    "Models, auth, join/claim/winner endpoints, real API swap"
  ),
  check.names = FALSE
)
kable(roadmap)
```

---

*Prepared as a working reference for the VELOOP Rewards Giveaway module build.
Section numbers referenced above correspond to the original task specification
document.*
