---
title: "VELOOP Rewards — Giveaway Module"
subtitle: "Full Architecture & Development Roadmap"
author: "VELOOP Rewards"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: flatly
    number_sections: true
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
```

Frontend architecture, data flow design, and a week-by-week execution plan for the
Giveaway Page, Banner, Participation, and Winner system.

---

# Full Folder Architecture

The project is split into two phases with two top-level folders: **frontend/** (build
first, fully mock-data driven) and **backend/** (build second, once the frontend is
approved). The key rule throughout: every component reads from `data/` or
`services/` — never hardcodes a prize name, fee, or status directly.

```
veloop-giveaway/
|
+-- frontend/
|   +-- public/
|   |   +-- assets/                    (prize images, icons from provided assets)
|   |
|   +-- src/
|   |   +-- components/
|   |   |   +-- GiveawayHero/
|   |   |   +-- GiveawayBanner/
|   |   |   +-- Countdown/
|   |   |   +-- GiveawayStats/
|   |   |   +-- PrizeCard/
|   |   |   +-- FeaturedGiveaways/
|   |   |   +-- HowToParticipate/
|   |   |   +-- WinnerSlider/
|   |   |   +-- WinnersTabs/
|   |   |   +-- WinnerCard/
|   |   |   +-- PreviousWinnerCard/
|   |   |   +-- PrizeClaimModal/
|   |   |   +-- JoinConfirmModal/
|   |   |   +-- BalanceIndicator/
|   |   |   +-- GiveawayRules/
|   |   |   +-- FAQ/
|   |   |   +-- TrustSection/
|   |   |   +-- GiveawayLoader/         (custom themed loader, sec 51-55)
|   |   |   +-- EmptyState/
|   |   |   +-- ErrorState/
|   |   |   +-- Skeletons/
|   |   |
|   |   +-- pages/
|   |   |   +-- GiveawayHome/           (main listing page)
|   |   |   +-- GiveawayDetails/        (/giveaway/:slug - individual page)
|   |   |   +-- NotFound/
|   |   |
|   |   +-- data/
|   |   |   +-- giveawayData.js         (mock API-shaped data)
|   |   |   +-- mockSession.js          (fake logged-in user, balances)
|   |   |   +-- mockWinners.js
|   |   |
|   |   +-- hooks/
|   |   |   +-- useCountdown.js
|   |   |   +-- useGiveawayStatus.js
|   |   |   +-- useBalanceCheck.js
|   |   |   +-- useGiveaway.js          (later wraps real fetch calls)
|   |   |
|   |   +-- context/
|   |   |   +-- UserContext.jsx         (mock auth/session state)
|   |   |
|   |   +-- services/
|   |   |   +-- giveawayApi.js          (stub functions -> real fetch later)
|   |   |
|   |   +-- utils/
|   |   |   +-- currencyValidation.js   (VEs/SVEs/Tokens rules, sec 89)
|   |   |   +-- maskUserId.js           (VE****42 style masking)
|   |   |   +-- formatTime.js
|   |   |
|   |   +-- styles/                     (global CSS variables, tokens)
|   |   +-- App.jsx
|   |   +-- main.jsx
|   |
|   +-- vite.config.js
|
+-- backend/                            (Phase 2 - do not start yet)
    +-- src/
    |   +-- controllers/
    |   |   +-- giveawayController.js
    |   |   +-- participationController.js
    |   |   +-- winnerController.js
    |   |   +-- claimController.js
    |   |   +-- adminGiveawayController.js
    |   +-- models/
    |   |   +-- Giveaway.js
    |   |   +-- Prize.js
    |   |   +-- GiveawayParticipation.js
    |   |   +-- GiveawayEntryTransaction.js
    |   |   +-- GiveawayWinner.js
    |   |   +-- PrizeClaim.js
    |   |   +-- FraudEvent.js
    |   |   +-- AuditLog.js
    |   +-- routes/
    |   +-- middleware/
    |   |   +-- authMiddleware.js
    |   |   +-- rateLimitMiddleware.js
    |   |   +-- validationMiddleware.js
    |   |   +-- fraudMiddleware.js
    |   |   +-- errorMiddleware.js
    |   +-- services/
    |   |   +-- giveawayService.js
    |   |   +-- participationService.js
    |   |   +-- balanceService.js
    |   |   +-- fraudService.js
    |   |   +-- winnerService.js
    |   +-- utils/
    |   +-- validators/
    |   +-- config/
    |   +-- app.js
    +-- server.js
```

---

# State & Data Flow Design

## UserContext

Holds `isLoggedIn`, `currentUserId`, and `balances` (VEs, SVEs, Tokens). Fully
mocked for now; swapped for real auth once the backend exists.

## services/giveawayApi.js

Exports functions such as `getCurrentGiveaways()`, `getGiveawayBySlug()`,
`joinGiveaway()`, and `submitClaim()`. Right now they return mock data behind a
fake delay (to honestly test loading states). Later, only the function bodies
change to real `fetch()` calls — nothing else in the app needs to change.

## useGiveawayStatus(giveaway)

A single hook that is the one source of truth for `ACTIVE` / `ENDED` /
`UPCOMING`, used by every component instead of scattering status checks across
the codebase.

> **Architectural rule:** the frontend is built exactly as if a real backend
> already exists. Components never see raw hardcoded values — only data
> returned from the `data/` and `services/` layers. This is what allows Phase 2
> (backend integration) to be a drop-in swap instead of a rewrite.

---

# Roadmap

Suggested pace: 3–4 weeks for the frontend phase, followed by a separate
backend phase once the frontend is reviewed and approved.

## Week 1 — Foundation

- Scaffold project (Vite + React), install dependencies, build the folder skeleton
- Write `giveawayData.js` and `mockSession.js` with realistic, API-shaped data (sections 36–38, 85 of the task doc)
- Build `UserContext`, `useCountdown`, and `useGiveawayStatus` hooks
- Build the Hero / Banner section (static layout first, no live logic yet)

## Week 2 — Core Home Page

- Wire the Countdown component to the real hook
- Build the Statistics section, Prize Cards grid, and Winner Slider
- Build the How-to-Participate timeline, Trust section, and FAQ accordion
- Build Winners Tabs and Previous Winners Tabs, including the correct empty state for an active giveaway that has no winners yet (section 21)

## Week 3 — Individual Giveaway Page + Join Flow

- Set up routing for `/giveaway/:slug`
- Build the Prize Information card, entry-fee display, and balance-check UI
- Build the Join Confirmation modal, success state, and already-joined state
- Build the login-required redirect flow for unauthenticated users

## Week 4 — Winner / Claim System + Polish

- Winner detection: `currentUserId === winner.userId`
- Claim modal with branching logic for physical prize vs. gift-card form, based on `prize.type`
- Claim states: submitted, processing, completed, expired
- Loading skeletons, error states, and empty states across all sections
- Full responsive pass: mobile -> tablet -> desktop
- Accessibility pass: labels, visible focus states, keyboard navigation
- Write the README, capture screenshots, deploy to Vercel

## Phase 2 — Backend (after frontend is approved / submitted)

- Scaffold the backend, define MongoDB models, build auth middleware
- Build the join endpoint with transaction handling and fraud checks
- Build winner-selection and prize-claim endpoints
- Swap the mock functions in `services/giveawayApi.js` for real fetch calls — this should be close to a drop-in replacement if Phase 1 was structured correctly

## Summary

```{r roadmap-table}
roadmap <- data.frame(
  Week = c("1", "2", "3", "4", "Phase 2"),
  Focus = c("Foundation", "Home page", "Detail page", "Claim + polish", "Backend"),
  `Key Deliverables` = c(
    "Project scaffold, mock data model, hooks, static banner",
    "Countdown, stats, prize cards, winner slider, tabs, FAQ",
    "Routing, prize info, join confirmation, login gate",
    "Claim system, loaders, responsive + a11y pass, deploy",
    "Models, auth, join/claim/winner endpoints, real API swap"
  ),
  check.names = FALSE
)
kable(roadmap)
```

---

*Prepared as a working reference for the VELOOP Rewards Giveaway module build.
Section numbers referenced above correspond to the original task specification
document.*

---

# Daily Execution Plan

> Based on the **Official Internship Regulations & Work Schedule** (PDF) issued by
> CEO Ayan Alam. Working hours: **9:30 AM – 6:15 PM, Monday – Friday only.**

## The PDF Cycle Rule

The PDF mandates a repeating 3-day professional work cycle throughout the internship:

```{r cycle-table}
cycle <- data.frame(
  `Day Type` = c(
    "Day 1 — Review Day",
    "Day 2 — Work Day",
    "Day 3 — Re-review Day",
    "Day 4+ — Repeat"
  ),
  Purpose = c(
    "Start → Work → Share → Review",
    "Improve → Fix → Develop",
    "Reshare → Re-review → Next Feedback",
    "Same cycle repeats throughout internship"
  ),
  `Key Rule` = c(
    "Share GitHub/live link, ask questions, request feedback",
    "NO new review requests — apply feedback and keep building",
    "Share updated progress, raise Day 2 unresolved questions",
    "Never repeat the same question; always try to solve yourself first"
  ),
  check.names = FALSE
)
kable(cycle)
```

> **Important:** Before asking any question, verify — Was this already answered?
> Was it in the project requirements? Have I tried solving it myself?

---

## Week 1 — Foundation (Days 1–5)

### Day 1 (Mon) — Scaffold & First Share `[REVIEW DAY]`

- Initialize Vite + React: `npm create vite@latest veloop-giveaway -- --template react`
- Install dependencies: `react-router-dom`, `date-fns`, CSS modules
- Create full folder skeleton: `components/`, `pages/`, `data/`, `hooks/`,
  `context/`, `services/`, `utils/`, `styles/`
- Write global CSS variables/tokens in `src/styles/`
- Start `giveawayData.js` with realistic, API-shaped mock data
- **End of day:** Push to GitHub → Share link → Ask questions → Request review

### Day 2 (Tue) — Deepen Foundation `[WORK DAY]`

- Complete `giveawayData.js` with full prize entries
- Write `mockSession.js` — fake logged-in user with VEs/SVEs/Tokens balances
- Write `mockWinners.js` — sample winner entries with masked user IDs
- Build `UserContext.jsx` — `isLoggedIn`, `currentUserId`, `balances`
- Build `useCountdown.js` hook — countdown to `giveaway.endDate`
- Build `useGiveawayStatus.js` — single source of truth for ACTIVE/ENDED/UPCOMING
- Apply all Day 1 review feedback
- **Do NOT request a new review today**

### Day 3 (Wed) — Static Banner + Re-review `[REVIEW DAY]`

- Build `GiveawayHero/` component — static layout, prize name from data
- Build `GiveawayBanner/` component — using data layer only
- Build `GiveawayLoader/`, `EmptyState/`, `ErrorState/` shells
- **End of day:** Reshare GitHub → Explain improvements → Ask Day 2 questions → Request re-review

### Day 4 (Thu) — Service Layer + Utils `[WORK DAY]`

- Apply all Day 3 feedback
- Build `BalanceIndicator/` component (reads from `UserContext`)
- Build `giveawayApi.js` service stubs: `getCurrentGiveaways()`,
  `getGiveawayBySlug()`, `joinGiveaway()`, `submitClaim()` with mock delay
- Write `currencyValidation.js`, `maskUserId.js`, `formatTime.js`

### Day 5 (Fri) — Hooks + Week 1 Wrap-up `[REVIEW DAY]`

- Connect `useGiveaway.js` to wrap all service calls
- Build `useBalanceCheck.js` hook
- Ensure zero hardcoded values across all components
- Light responsive pass on Banner + Hero; run linter
- **End of day:** Reshare GitHub → Summarize Week 1 → Ask questions → Request re-review

---

## Week 2 — Core Home Page (Days 6–10)

### Day 6 (Mon) — Countdown + Stats `[REVIEW DAY]`

- Wire `Countdown/` to `useCountdown` hook — live ticking display
- Build `GiveawayStats/` — participant count, prize count, total value from data
- Begin `PrizeCard/` — prize image, name, fee, status badge
- Apply all Week 1 feedback
- **End of day:** Share → Ask → Review

### Day 7 (Tue) — Prize Cards + Grid `[WORK DAY]`

- Complete `PrizeCard/` with hover effects and status-based styling
- Build `FeaturedGiveaways/` — grid layout using `getCurrentGiveaways()`
- Build `Skeletons/` — loading skeleton for `PrizeCard`
- Apply Day 6 feedback

### Day 8 (Wed) — Winner Slider + Tabs `[REVIEW DAY]`

- Build `WinnerSlider/` — auto-scrolling slider of latest winners
- Build `WinnersTabs/` — "Active Giveaway Winners" / "Previous Winners" tabs
- Build `WinnerCard/` and `PreviousWinnerCard/` with masked userId display
- Handle correct empty state for active giveaway with no winners yet (Section 21)
- **End of day:** Reshare → Explain → Ask Day 7 questions → Request re-review

### Day 9 (Thu) — How-to + Trust + FAQ `[WORK DAY]`

- Apply Day 8 feedback
- Build `HowToParticipate/` — step-by-step visual timeline
- Build `TrustSection/` — trust signals and stats
- Build `FAQ/` — accordion-style expandable Q&A
- Build `GiveawayRules/` — rules display component

### Day 10 (Fri) — Home Page Assembly `[REVIEW DAY]`

- Connect `GiveawayHome` page — assemble all Week 2 components
- Mobile-first responsive pass across all Week 2 components
- **End of day:** Demo countdown, stats, cards, slider → Ask questions → Request re-review

---

## Week 3 — Individual Giveaway Page + Join Flow (Days 11–15)

### Day 11 (Mon) — Routing + Detail Page Shell `[REVIEW DAY]`

- Set up routing: `/` → `GiveawayHome`, `/giveaway/:slug` → `GiveawayDetails`
- Build `GiveawayDetails/` page shell connected to `getGiveawayBySlug(slug)`
- Apply all Week 2 feedback
- **End of day:** Share routing demo → Ask → Review

### Day 12 (Tue) — Prize Info + Entry Fee `[WORK DAY]`

- Apply Day 11 feedback
- Build Prize Information card on detail page
- Build entry-fee display section (reads fee from data, never hardcoded)
- Wire `useBalanceCheck` — show sufficient / insufficient balance UI

### Day 13 (Wed) — Join Modal `[REVIEW DAY]`

- Build `JoinConfirmModal/` — confirmation step before spending tokens
- Join success state — updated balance display
- Already-joined state — "You're already in this giveaway"
- Build login-required redirect flow for unauthenticated users
- **End of day:** Demo join flow end-to-end → Ask Day 12 questions → Request re-review

### Day 14 (Thu) — Detail Page Polish `[WORK DAY]`

- Apply Day 13 feedback
- Connect detail page to full data flow: status, countdown, prize, join state
- Responsive pass on `GiveawayDetails` page

### Day 15 (Fri) — Week 3 Review `[REVIEW DAY]`

- Full routing test: `/` and `/giveaway/:slug` flows
- Test logged-in vs. logged-out states; test join flow: pending → success → already-joined
- **End of day:** Reshare Week 3 demo → Ask questions → Request re-review

---

## Week 4 — Winner / Claim System + Polish (Days 16–20)

### Day 16 (Mon) — Winner Detection `[REVIEW DAY]`

- Implement winner detection: `currentUserId === winner.userId`
- Show "You won!" banner/state when the current user is the winner
- Apply all Week 3 feedback
- **End of day:** Share winner detection demo → Ask → Review

### Day 17 (Tue) — Claim Modal `[WORK DAY]`

- Apply Day 16 feedback
- Build `PrizeClaimModal/` with branching logic by `prize.type`:
  - `'physical'` → shipping address form
  - `'gift-card'` → gift card details form
- Claim states: `submitted` → `processing` → `completed` / `expired`

### Day 18 (Wed) — Loading + Error + Empty States `[REVIEW DAY]`

- Build/complete loading skeletons for all major sections
- Build error states for failed API calls; build empty states for all sections
- Every async flow: loading → data / error / empty
- **End of day:** Reshare with all states working → Ask Day 17 questions → Request re-review

### Day 19 (Thu) — Responsive + Accessibility Pass `[WORK DAY]`

- Apply Day 18 feedback
- Full responsive pass: mobile → tablet → desktop (all pages and components)
- Accessibility: `alt` text on all images, labels on all interactive elements,
  visible focus states, semantic HTML, modal focus trapping

### Day 20 (Fri) — README + Deploy + Final Review `[REVIEW DAY]`

- Write `README.md`: overview, tech stack, folder structure, setup, screenshots
- Deploy to Vercel: `vercel --prod`; final cross-browser test
- **End of day:** Share live Vercel link + GitHub → Request final frontend review
- **Await explicit approval before starting Phase 2**

---

## Phase 2 — Backend Plan

> **Do not start Phase 2 until the frontend is approved.**

```{r backend-table}
backend <- data.frame(
  Step = 1:8,
  Task = c(
    "Scaffold Node.js/Express backend",
    "Define MongoDB models: Giveaway, Prize, GiveawayParticipation, GiveawayEntryTransaction, GiveawayWinner, PrizeClaim, FraudEvent, AuditLog",
    "Build authMiddleware.js",
    "Build join endpoint with transaction handling and fraud checks",
    "Build winner-selection endpoint",
    "Build prize-claim endpoint",
    "Build admin giveaway controller",
    "Swap mock functions in services/giveawayApi.js for real fetch() calls (drop-in swap)"
  )
)
kable(backend)
```

---

## Daily Checklist

Every working day should follow this checklist:

**Morning (9:30 AM)**

- Review yesterday's progress and plan 3–4 key deliverables for today
- Check for any new feedback received in the group

**During Work (9:30 AM – 6:15 PM)**

- Components always read from `data/` or `services/` — never hardcode values
- Note any blockers or questions; do not ask immediately — resolve on the next Review Day

**End of Day**

- Push all code to GitHub
- On **Review Days**: Share link, explain progress, ask questions, request feedback
- On **Work Days**: Continue improving — do NOT request a new review

---

## Key Architectural Rules

1. **No hardcoded values** — every prize name, fee, and status comes from `data/` or `services/`
2. **`useGiveawayStatus` is the single source of truth** for ACTIVE/ENDED/UPCOMING across all components
3. **Service layer is mock now, real later** — function signatures stay identical; only bodies change in Phase 2
4. **Frontend built as if the backend exists** — Phase 2 becomes a drop-in swap, not a rewrite
5. **Group polls are mandatory** — respond to all official polls within the given time

---

*Daily plan aligned with official PDF regulations issued by CEO Ayan Alam, VELOOP Rewards.*
